---
title: replicaton assigment
team: the Beginners
date: october 2019
authors: Edward Garcia, Paula Muñoz, Jan Melendez y Alicia Figueroa
---
```{r}
#library

library(ggplot2)
library(knitr)
library(dplyr)
library(reshape2)
library(energy)
```
## Questions

1. How many cell-lines are contained in the data?

Hay 288 líneas de células contenidas en la data.

```{r}
data <- read.csv("rawPharmacoData.csv")

length( levels( data$cellLine ) )
```

2. What drug concentrations were used in each study?

8 CCLE y 32 GDSC

```{r}
tapply( data$concentration, data$study, function(x){
        length( unique( x ) )
    })
```

3. Histograms, appart from telling how is the data
distributed, can also make evident potential
problems with the data. Plot a histogram
of drug viabilities. Does it look as one would
expect from the description of the data?

No porque debido a que las drogas son anti cáncer no debe de haber tanta bioabilidad.

```{r}
ggplot( pharmacoData, aes( log2(viability) ) ) +
    geom_histogram(fill = "white", colour="black") +
    facet_wrap(~study)
```

4. How many viability data points are within the
expected range according to the definition of viability (e.g. above 0 
and below 100)? Try to come up with explanations about
the values that are out of range. Are these due to technical
issues? Biology?

27611.
Los valores que salen del rango pueden explicarse debido a la diferencia que hay a
consecuencia del tratamiento. Se esperan que las células cuyos valores están por debajo de 100
tengan issues técnicos de salud debido al margen de error que hay en viabilidad. Las drogas no
afectaron la proliferación en células cuyos valores eran menores a 100.

```{r}
sum( data$viability > 0 & data$viability < 100)
```

5. Read the csv file containing the summarized data files. What kind
of variables are in the data? What does each column represents?

cellLine, drug, ic50_CCLE, auc_CCLE, ic50_GDSC y auc_GDSC.

```{r}
datasum <- read.csv("summarizedPharmacoData.csv")

str(datasum)
```

6. Plot a histogram of the viability scores as a function of the drug
doses. Are stronger drug concentrations consistent with lower viability scores?

No todos, como la droga placlitaxel que es una de las que menor viabilidad tiene.
```{r}
ggplot( pharmacoData, aes( viability, group=drug, colour=drug) ) +
    geom_density(fill="white", lwd=2, alpha=0.1) + xlim(0, 170)
```
