---
title: replicaton assigment
team: the Beginners
date: october 2019
authors: Edward Garcia, Paula Muñoz, Jan Melendez y Alicia Figueroa
---
```{r}
#library

library(ggplot2)
library(knitr)
library(dplyr)
library(reshape2)
library(energy)
```
## Questions

1. How many cell-lines are contained in the data?
There are 288 cell lines contained in the data.

```{r}
data <- read.csv("rawPharmacoData.csv")

length( levels( data$cellLine ) )
```

2. What drug concentrations were used in each study?
in each study there were used 32 GDSC concentrations and 8 CClE concentrations.

```{r}
tapply( data$concentration, data$study, function(x){
        length( unique( x ) )
    })
```

3. Histograms, appart from telling how is the data
distributed, can also make evident potential
problems with the data. Plot a histogram
of drug viabilities. Does it look as one would
expect from the description of the data?
```{r}
ggplot( pharmacoData, aes( log2(viability) ) ) +
    geom_histogram(fill = "white", colour="black") +
    facet_wrap(~study)
```

4. How many viability data points are within the
expected range according to the definition of viability (e.g. above 0 
and below 100)? Try to come up with explanations about
the values that are out of range. Are these due to technical
issues? Biology?
```{r}
sum( data$viability > 0 & data$viability < 100)
```

5. Read the csv file containing the summarized data files. What kind
of variables are in the data? What does each column represents?
```{r}
datasum <- read.csv("summarizedPharmacoData.csv")

str(datasum)
```
6. Plot a histogram of the viability scores as a function of the drug
doses. Are stronger drug concentrations consistent with lower viability scores?
```{r}
ggplot( pharmacoData, aes( viability, group=drug, colour=drug) ) +
    geom_density(fill="white", lwd=2, alpha=0.1) + xlim(0, 170)
```
