---
title: replicaton assigment
team: the Beginners
date: october 2019
authors: Edward Garcia, Paula Muñoz, Jan Melendez y Alicia Figueroa
---
```{r}
#library

library(ggplot2)
library(knitr)
library(dplyr)
library(reshape2)
library(energy)
```
## Questions

1. How many cell-lines are contained in the data?
There are 288 cell lines contained in the data.

```{r}
length( levels( data$cellLine ) )
```

2. What drug concentrations were used in each study?
in each study there were used 32 GDSC concentrations and 8 CClE concentrations.

```{r}
tapply( data$concentration, data$study, function(x){
        length( unique( x ) )
    })
```

3. Histograms, appart from telling how is the data
distributed, can also make evident potential
problems with the data. Plot a histogram
of drug viabilities. Does it look as one would
expect from the description of the data?
```
```

4. How many viability data points are within the
expected range according to the definition of viability (e.g. above 0 
and below 100)? Try to come up with explanations about
the values that are out of range. Are these due to technical
issues? Biology?

5. Read the csv file containing the summarized data files. What kind
of variables are in the data? What does each column represents?

6. Plot a histogram of the viability scores as a function of the drug
doses. Are stronger drug concentrations consistent with lower viability scores?
```{r}
#Your code goes here


data <- read.csv("rawPharmacoData.csv")
datasum <- read.csv("summarizedPharmacoData.csv")

str(data)

dataCCLE <- data[data$study == "CCLE",]
dataGDSC <- data[data$study == "GDSC",]
unique(dataCCLE$concentration)




ggplot( pharmacoData, aes( log2(viability) ) ) +
    geom_histogram(fill = "white", colour="black") +
    facet_wrap(~study)

sum( data$viability > 0 & data$viability < 100)

str(datasum)

ggplot( pharmacoData, aes( viability, group=drug, colour=drug) ) +
    geom_density(fill="white", lwd=2, alpha=0.1) + xlim(0, 170)

ggplot(aes(x=auc_GDSC, y=auc_CCLE), data=cellLinesSummary) +
    geom_point(cex=0.5) +
    facet_wrap(facets=~drug) +
    xlab("GDSC AUC") +
    ylab("CCLE AUC")

cor.coef <- round(cor(datasum$auc_GDSC, datasum$auc_CCLE),2)
ggplot(aes(x=auc_GDSC, y=auc_CCLE), data=cellLinesSummary) +
    geom_point(cex=0.5) +
    facet_wrap(facets=~drug) +
    ggtitle(paste0("Correlation coefficient = ", cor.coef))+ 
    xlab("GDSC AUC") +
    ylab("CCLE AUC") +
    geom_smooth(method='lm', se=FALSE)

ggplot(aes(x=ic50_GDSC, y=ic50_CCLE), data=cellLinesSummary) +
    geom_point(cex=0.5) +
    facet_wrap(facets=~drug) +
    xlab("GDSC ic50") +
    ylab("CCLE ic50")

cor.coef <- round(cor(datasum$ic50_GDSC, datasum$ic50_CCLE),2)
ggplot(aes(x=ic50_GDSC, y=ic50_CCLE), data=cellLinesSummary) +
    geom_point(cex=0.5) +
    facet_wrap(facets=~drug) +
    ggtitle(paste0("Correlation coefficient = ", cor.coef))+ 
    xlab("GDSC ic50") +
    ylab("CCLE ic50") +
    geom_smooth(method='lm', se=FALSE)


drugCorrs <- cellLinesSummary %>% 
    group_by(drug) %>% summarise(Pearson_ic50=cor(-log10(ic50_GDSC/10^6),-log10(ic50_CCLE/10^6), method="pearson"),
                                 Spearman_ic50=cor(-log10(ic50_GDSC/10^6),-log10(ic50_CCLE/10^6), method="spearman"))
drugCorrs <- melt(drugCorrs)
colnames(drugCorrs) <- c("Drug", "Measure", "Correlation")

drugCorrs_IC50 <- drugCorrs[grep("ic50", drugCorrs$Measure),]
ggplot(data=drugCorrs_IC50, aes(x=Drug, y=Correlation, fill=Measure, group=Measure)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_grey()

drugCorrss <- cellLinesSummary %>% 
    group_by(drug) %>% summarise(Pearson_auc=cor(-log10(auc_GDSC/10^6),-log10(auc_CCLE/10^6), method="pearson"),
                                 Spearman_auc=cor(-log10(auc_GDSC/10^6),-log10(auc_CCLE/10^6), method="spearman"))
drugCorrss <- melt(drugCorrss)
colnames(drugCorrss) <- c("Drug", "Measure", "Correlation")

drugCorrs_auc <- drugCorrss[grep("ic50", drugCorrss$Measure),]
ggplot(data=drugCorrs_auc, aes(x=Drug, y=Correlation, fill=Measure, group=Measure)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_grey()

dcor.t(datasum$ic50_GDSC,datasum$ic50_CCLE)
dcor.ttest(datasum$ic50_GDSC,datasum$ic50_CCLE)
```
