---
title: replicaton assigment
team: the Beginners
date: october 2019
authors: Edward Garcia, Paula Muñoz, Jan Melendez y Alicia Figueroa
---
```{r}
#library

library(ggplot2)
library(knitr)
library(dplyr)
library(reshape2)
library(energy)
```
## Questions

1. Create a scatterplot for each drug comparing the AUC in GDSC and CCLE for all cell lines (hint: code from Tutorial 2 may help).    

2. Calculate correlation coefficients of the AUC in GDSC and CCLE for each drug (hint: code from Tutorial 2 may help). 

3. Based on the scatterplot and correlation values, would you say that they tend to agree? Why or why not?

4. Does the AUC or IC50 suggest more agreement between the studies? 
No se ven buenas condiciones entre estudios

5. Which drug do you think shows the most consistency between the studies? How about the least? 
PD= 0325901, AZD0530 y 17-AAG tienen mayor consistencia entre Spearman y Pearson en los
dos estudios.

6. If you calculated more than one type of correlation coefficient (for example Pearson and Spearman), how do they differ? Which do you think is a better summary of the consistency between the two studies? 
Los resultados muestran que la relación de Pearson tiene mayor consistencia ya que no varían
mucho.

7. We have explored Pearson and Spearman correlation, but what about other correlation measures? For example, you could try out distance correlation, which is sensitive to nonlinear relationships. You can find this measure in the `energy` R package, which you'll need to install and load with the following commands:

    ```{r, eval=FALSE}
    

    
    install.packages("energy")
    load(energy)
    ```

    Then, you can compute distance correlation with the `dcor()` function. How does this correlation measure compare to Pearson and Spearman? Do your conclusions about the agreement between the two studies change at all using this measure?

## codigo

```{r}
ggplot( pharmacoData, aes( viability, group=drug, colour=drug) ) +
    geom_density(fill="white", lwd=2, alpha=0.1) + xlim(0, 170)

ggplot(aes(x=auc_GDSC, y=auc_CCLE), data=cellLinesSummary) +
    geom_point(cex=0.5) +
    facet_wrap(facets=~drug) +
    xlab("GDSC AUC") +
    ylab("CCLE AUC")

cor.coef <- round(cor(datasum$auc_GDSC, datasum$auc_CCLE),2)
ggplot(aes(x=auc_GDSC, y=auc_CCLE), data=cellLinesSummary) +
    geom_point(cex=0.5) +
    facet_wrap(facets=~drug) +
    ggtitle(paste0("Correlation coefficient = ", cor.coef))+ 
    xlab("GDSC AUC") +
    ylab("CCLE AUC") +
    geom_smooth(method='lm', se=FALSE)

ggplot(aes(x=ic50_GDSC, y=ic50_CCLE), data=cellLinesSummary) +
    geom_point(cex=0.5) +
    facet_wrap(facets=~drug) +
    xlab("GDSC ic50") +
    ylab("CCLE ic50")

cor.coef <- round(cor(datasum$ic50_GDSC, datasum$ic50_CCLE),2)
ggplot(aes(x=ic50_GDSC, y=ic50_CCLE), data=cellLinesSummary) +
    geom_point(cex=0.5) +
    facet_wrap(facets=~drug) +
    ggtitle(paste0("Correlation coefficient = ", cor.coef))+ 
    xlab("GDSC ic50") +
    ylab("CCLE ic50") +
    geom_smooth(method='lm', se=FALSE)


drugCorrs <- cellLinesSummary %>% 
    group_by(drug) %>% summarise(Pearson_ic50=cor(-log10(ic50_GDSC/10^6),-log10(ic50_CCLE/10^6), method="pearson"),
                                 Spearman_ic50=cor(-log10(ic50_GDSC/10^6),-log10(ic50_CCLE/10^6), method="spearman"))
drugCorrs <- melt(drugCorrs)
colnames(drugCorrs) <- c("Drug", "Measure", "Correlation")

drugCorrs_IC50 <- drugCorrs[grep("ic50", drugCorrs$Measure),]
ggplot(data=drugCorrs_IC50, aes(x=Drug, y=Correlation, fill=Measure, group=Measure)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_grey()

drugCorrss <- cellLinesSummary %>% 
    group_by(drug) %>% summarise(Pearson_auc=cor(-log10(auc_GDSC/10^6),-log10(auc_CCLE/10^6), method="pearson"),
                                 Spearman_auc=cor(-log10(auc_GDSC/10^6),-log10(auc_CCLE/10^6), method="spearman"))
drugCorrss <- melt(drugCorrss)
colnames(drugCorrss) <- c("Drug", "Measure", "Correlation")

drugCorrs_auc <- drugCorrss[grep("ic50", drugCorrss$Measure),]
ggplot(data=drugCorrs_auc, aes(x=Drug, y=Correlation, fill=Measure, group=Measure)) +
  geom_bar(stat="identity", position=position_dodge(), colour="black") + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_fill_grey()

dcor.t(datasum$ic50_GDSC,datasum$ic50_CCLE)
dcor.ttest(datasum$ic50_GDSC,datasum$ic50_CCLE)
```
